### 2018-10-26 Sections/cryptowars.tex
Minor edits

Private- (or symmetric-) key cryptography is perhaps the most basic (and useful) cryptographic primitive, enabling encryption of a channel between two parties who share a secret key\index{Private key} -- a random bit-string of length determined by the encryption algorithm. The same secret key is employed for both encryption and decryption operations (hence `symmetric'), making it of utmost importance that it be retained secret.

@@

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic security} as opposed to computational security\index{Computational security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad}. This protocol requires Alice and Bob to share a random secret key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

@@

Needless to say, the requirement for keys of the same length as the plaintexts, which cannot be reused, raises the obvious criticism that now secret key-sharing is as difficult as sharing a secret message in the first place. This reduces the problem of perfect secrecy of arbitrary messages to the secrecy of shared randomness.

@@

While private-key cryptography solves the problem of end-to-end cryptography, it has one main downfall -- how does one share a private key between two parties? After all, if we had the ability to secretly share keys between ourselves, wouldn't we just use that same method to directly communicate, bypassing the unnecessary cryptographic protocol?

Public- (or asymmetric-) key cryptography addresses this issue by replacing the private key with two keys (known as a key-pair\index{Key-pair}), one used solely for \textit{encryption}, the other solely for \textit{decryption}. Importantly, these two keys are non-trivially related and cannot be efficiently computed from one another. To send a message to a friend I can send him my encryption (public) key that he is only able to use for preparing an encrypted message for me. No security is required when sharing the public key since an eavesdropper can't use it for decryption. Finally, I am able to decrypt the message using my decryption (private) key, which I kept completely to myself and never shared with anyone.

@@

Digital signatures can be easily implemented using the RSA protocol\index{RSA protocol}, by reversing the roles of the public and private keys. Now the public key can only be used for decrypting a message, and the private key can only be used for encrypting it. As before, it is computationally hard to infer one from the other. The protocol for sending and verifying a digitally signed message is shown in Alg.~\ref{alg:dig_sig}.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash functions}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$digest=SHA256(message)$
	\item Alice encrypts the digest using her private key. This forms the `digital signature',\\
	\vspace{1mm} 
	$signature = RSAEncrypt(digest,privateKey)$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$signedMessage = \{message,signature\}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$hash=SHA256(message)$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$decryptedHash =$\\
	$RSADecrypt(signature,publicKey)$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$if(decryptedHash=hash)$\\
	$\,\,return(pass)$\\
	$else$\\
	$\,\,return(fail)$
	\item $\Box$
\end{enumerate}
}
\end{mdframed}
\captionspacealg \caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

The key point from the security perspective is that the private key cannot be efficiently inferred from the public key. So although everyone has access to Alice's public key, no one is able to counterfeit messages since they cannot create encrypted signatures without access to her private key -- signatures can be easily verified but not created.

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key cryptography}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private key lengths will need to be doubled to maintain an equivalent level of security against brute-force attacks.

@@

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private keys to be retrieved from public keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O((\log n)^2(\log\log n)(\log\log\log n)).
\end{align}
Compare this with the classical case given in Eq.~(\ref{eq:GNFS_scaling}).

@@

\dropcap{A}s quantum physics can compromise some important aspects of classical cryptography, can it perhaps be similarly exploited to make new cryptosystems that are immune even to quantum adversaries? Thankfully the answer is yes\ldots at least some of the time.

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number splitting attack}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Intercept-resend attack}, but not of an intercept-resend\index{Intercept-resend attack} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis, thereby recovering the associated secret key bit.

@@

Here Alice and Bob share a short secret key $k$ of length $m$, and wish to communicate a message $j$ of length $n$. The secret key might be established via conventional QKD. First off, they agree upon a set of Haar-random unitaries\index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $2^m$ keys. This needn't be performed in secret. Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret key, yielding the encoded state,
\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

>>>>

Private- (or symmetric-) key cryptography is perhaps the most basic (and useful) cryptographic primitive, enabling encryption of a channel between two parties who share a secret-key\index{Private-key} -- a random bit-string of length determined by the encryption algorithm. The same secret-key is employed for both encryption and decryption operations (hence `symmetric'), making it of utmost importance that it be retained secret.

@@

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic security} as opposed to computational security\index{Computational security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad}. This protocol requires Alice and Bob to share a random secret-key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

@@

Needless to say, the requirement for keys of the same length as the plaintexts, which cannot be reused, raises the obvious criticism that now secret-key-sharing is as difficult as sharing a secret message in the first place. This reduces the problem of perfect secrecy of arbitrary messages to the secrecy of shared randomness.

@@

While private-key cryptography solves the problem of end-to-end cryptography, it has one main downfall -- how does one share a private-key between two parties? After all, if we had the ability to secretly share keys between ourselves, wouldn't we just use that same method to directly communicate, bypassing the unnecessary cryptographic protocol?

Public- (or asymmetric-) key cryptography addresses this issue by replacing the private-key with two keys (known as a key-pair\index{Key-pair}), one used solely for \textit{encryption}, the other solely for \textit{decryption}. Importantly, these two keys are non-trivially related and cannot be efficiently computed from one another. To send a message to a friend I can send him my encryption (public) key that he is only able to use for preparing an encrypted message for me. No security is required when sharing the public-key since an eavesdropper can't use it for decryption. Finally, I am able to decrypt the message using my decryption (private) key, which I kept completely to myself and never shared with anyone.

@@

Digital signatures can be easily implemented using the RSA protocol\index{RSA protocol}, by reversing the roles of the public and private-keys. Now the public-key can only be used for decrypting a message, and the private-key can only be used for encrypting it. As before, it is computationally hard to infer one from the other. The protocol for sending and verifying a digitally signed message is shown in Alg.~\ref{alg:dig_sig}.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash functions}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$digest=SHA256(message)$
	\item Alice encrypts the digest using her private-key. This forms the `digital signature',\\
	\vspace{1mm} 
	$signature = RSAEncrypt(digest,privateKey)$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$signedMessage = \{message,signature\}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$hash=SHA256(message)$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$decryptedHash =$\\
	$RSADecrypt(signature,publicKey)$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$if(decryptedHash=hash)$\\
	$\,\,return(pass)$\\
	$else$\\
	$\,\,return(fail)$
	\item $\Box$
\end{enumerate}
}
\end{mdframed}
\captionspacealg \caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

The key point from the security perspective is that the private-key cannot be efficiently inferred from the public-key. So although everyone has access to Alice's public-key, no one is able to counterfeit messages since they cannot create encrypted signatures without access to her private-key -- signatures can be easily verified but not created.

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key cryptography}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private-key lengths will need to be doubled to maintain an equivalent level of security against brute-force attacks.

@@

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private-keys to be retrieved from public-keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O((\log n)^2(\log\log n)(\log\log\log n)).
\end{align}
Compare this with the classical case given in Eq.~(\ref{eq:GNFS_scaling}).

@@

\dropcap{A}{s} quantum physics can compromise some important aspects of classical cryptography, can it perhaps be similarly exploited to make new cryptosystems that are immune even to quantum adversaries? Thankfully the answer is yes\ldots at least some of the time.

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number splitting attack}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Intercept-resend attack}, but not of an intercept-resend\index{Intercept-resend attack} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis, thereby recovering the associated secret-key bit.

@@

Here Alice and Bob share a short secret-key $k$ of length $m$, and wish to communicate a message $j$ of length $n$. The secret-key might be established via conventional QKD. First off, they agree upon a set of Haar-random unitaries\index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $2^m$ keys. This needn't be performed in secret. Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret-key, yielding the encoded state,
\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

### 2018-10-26 Sections/encrypted_cloud_quantum_computing.tex
Minor edits

\comment{A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, {\sc KeyGen}, an encryption algorithm, {\sc Encrypt}, an evaluation algorithm, {\sc Evaluate}, and a decryption algorithm, {\sc Decrypt}. The four algorithms have the following inputs and outputs:
\begin{itemize}
\item 	 {\sc KeyGen}$(\lambda)$: Takes as input a security parameter $\lambda$, and outputs a public key $pk$, and a secret key $sk$.
\item {\sc Encrypt}$(pk, \pi_i)$: Takes as input $pk$, and a plaintext $\pi_i$. It outputs a ciphertext $\psi_i$.
\item {\sc Evaluate}$(pk, C, \Psi)$: Takes as input $pk$, a permitted circuit $C$, and $\Psi=(\psi_1,\ldots, \psi_t)$. It outputs a ciphertext $\psi$.
\item {\sc Decrypt}$(sk,\psi)$: Takes as input $sk$, and $\psi$ and outputs $C(\pi_1,\ldots, \pi_t)$.
\end{itemize}
The computational complexity of all these algorithms must be polynomial in $\lambda$, and in the case of the evaluation algorithm, polynomial in the size of the evaluation circuit $C$. The condition that {\sc Decrypt}$(sk,\psi)$ outputs $C(\pi_1,\ldots, \pi_t)$ is a condition known as correctness which we require of the homomorphic encryption scheme. Furthermore, we also require ciphertext size and decryption time to be upper bounded by a function of the security parameter $\lambda$, independently of $C$. This last condition is known as compactness, and is necessary to exclude trivial schemes such as that which decrypts the ciphertexts first, and then apply $C$.}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PolarisationKeyEncoding($S$,$k$):
\begin{enumerate}
    \item Alice meditates upon, but needn't actually prepare the state,
    \begin{align}
    \ket\psi_\mathrm{number} = \ket{S_1,\dots,S_m},    
    \end{align}
    where,
    \begin{align}
S_i\in\{0,1\},
    \end{align}
is the photon-number of the $i$th mode.
   \item Alice makes the substitutions from the photon-number basis into the polarisation basis, 
   \begin{align}
   \ket{0}&\to\ket{H}, \nonumber \\
   \ket{1}&\to\ket{V},
   \end{align}
   to obtain $\ket\psi_\mathrm{pol}$, containing $m$ photons in total, one per mode.
   \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
   \begin{align}
    k\in(0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same polarisation rotation (using wave-plates), of angle $k$, to each mode,
   \begin{align}
   \ket\psi_\mathrm{enc} = \hat{R}(k)^{\otimes m}\ket\psi_\mathrm{pol},
   \end{align}
   where,
   \begin{align}
   \hat{R}(\theta) = \left(\begin{array}{cc}
\cos\theta & -\sin\theta \\
\sin\theta & \cos\theta \end{array}\right).
   \end{align}
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U} \ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat{R}(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item Alice applies polarisation filters to $\ket\psi_\mathrm{comp}$, discarding horizontally polarised photons.
    \item The remaining vertically polarised state is Alice's unencrypted output of the computation.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics, using polarisation-key encoding.} \label{alg:homo_LO}
\end{table}

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.425\textwidth]{BS_homo}
\captionspacefig \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

Like polarisation rotations, uniform phase-shifts commute through linear optics networks, as per Eq.~(\ref{eq:LO_key_commute}), and thus the protocol has similar mathematical structure to the photonic case. Now the phase-shift angle, $\phi$, acts as Alice's private key, which she applies uniformly to all input modes, applying inverse uniform phase-shifts after the computation to decrypt the state. The full algorithm is given in Alg.~\ref{alg:homo_coherent_LO}.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PhaseKeyEncoding($\vec\alpha$,$k$):
\begin{enumerate}
    \item Alice prepares the input multi-mode coherent state,
    \begin{align}
    \ket\psi_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m}.
    \end{align}
    \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
    \begin{align}
    k\in (0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same phase-shift, of angle $k$, to each mode,
    \begin{align}
    \ket\psi_\mathrm{enc} = \hat\Phi(k)^{\otimes m}\ket\psi_\mathrm{in},
    \end{align}
    where,
    \begin{align}
    \hat\Phi(\phi) = e^{i\phi\hat{n}},
    \end{align}
    is the phase-shift operator.
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat\Phi(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item The resulting state is,
    \begin{align}
    \ket\psi_\mathrm{comp} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m},
    \end{align}
    where,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on coherent state passive linear optics, using phase-key encoding.} \label{alg:homo_coherent_LO}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DisplacementKeyEncoding($\ket\psi$,$k$):
\begin{enumerate}
    \item Alice prepares the $m$-mode state $\ket\psi$.
    \item Alice chooses a set of independent complex displacement amplitudes as her private key,
    \begin{align}
    k=\{\alpha_1,\dots,\alpha_m\}.
    \end{align}
    \item Alice applies the displacements to each mode, yielding her encrypted state,
    \begin{align}
    \ket\psi_\mathrm{enc} = \left[\bigotimes_{i=1}^m \hat{D}_i(\alpha_i)\right] \ket\psi,
    \end{align}
    where $\hat{D}_i(\alpha_i)$ is the displacement operator for the $i$th mode, with displacement amplitude $\alpha_i$.
    \item Alice sends the encrypted state to Bob.
    \item Bob applies the computation $\hat{U}$,
    \begin{align}
    \ket\psi_\mathrm{enc\, comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns the encrypted computed state to Alice.
    \item Alice calculates the inverse displacement amplitudes $\vec\beta$,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item Alice applies the inverse displacements to each mode,
    \begin{align}
    \ket\psi_\mathrm{comp} &= \left[\bigotimes_{i=1}^m \hat{D}^\dag_i(\beta_i)\right] \ket\psi_\mathrm{enc\, comp} \nonumber \\
    &= \hat{U}\ket\psi,
    \end{align}
    \item $\ket\psi_\mathrm{comp}$ is the unencrypted computed output state.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption using displacement-key encoding.} \label{alg:homo_disp_LO}
\end{table}

>>>>

\comment{A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, {\sc KeyGen}, an encryption algorithm, {\sc Encrypt}, an evaluation algorithm, {\sc Evaluate}, and a decryption algorithm, {\sc Decrypt}. The four algorithms have the following inputs and outputs:
\begin{itemize}
\item 	 {\sc KeyGen}$(\lambda)$: Takes as input a security parameter $\lambda$, and outputs a public-key $pk$, and a secret-key $sk$.
\item {\sc Encrypt}$(pk, \pi_i)$: Takes as input $pk$, and a plaintext $\pi_i$. It outputs a ciphertext $\psi_i$.
\item {\sc Evaluate}$(pk, C, \Psi)$: Takes as input $pk$, a permitted circuit $C$, and $\Psi=(\psi_1,\ldots, \psi_t)$. It outputs a ciphertext $\psi$.
\item {\sc Decrypt}$(sk,\psi)$: Takes as input $sk$, and $\psi$ and outputs $C(\pi_1,\ldots, \pi_t)$.
\end{itemize}
The computational complexity of all these algorithms must be polynomial in $\lambda$, and in the case of the evaluation algorithm, polynomial in the size of the evaluation circuit $C$. The condition that {\sc Decrypt}$(sk,\psi)$ outputs $C(\pi_1,\ldots, \pi_t)$ is a condition known as correctness which we require of the homomorphic encryption scheme. Furthermore, we also require ciphertext size and decryption time to be upper bounded by a function of the security parameter $\lambda$, independently of $C$. This last condition is known as compactness, and is necessary to exclude trivial schemes such as that which decrypts the ciphertexts first, and then apply $C$.}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PolarisationKeyEncoding($S$,$k$):
\begin{enumerate}
    \item Alice meditates upon, but needn't actually prepare the state,
    \begin{align}
    \ket\psi_\mathrm{number} = \ket{S_1,\dots,S_m},    
    \end{align}
    where,
    \begin{align}
S_i\in\{0,1\},
    \end{align}
is the photon-number of the $i$th mode.
   \item Alice makes the substitutions from the photon-number basis into the polarisation basis, 
   \begin{align}
   \ket{0}&\to\ket{H}, \nonumber \\
   \ket{1}&\to\ket{V},
   \end{align}
   to obtain $\ket\psi_\mathrm{pol}$, containing $m$ photons in total, one per mode.
   \item Alice chooses a random private-key $k$ as a real number from the uniform distribution,
   \begin{align}
    k\in(0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same polarisation rotation (using wave-plates), of angle $k$, to each mode,
   \begin{align}
   \ket\psi_\mathrm{enc} = \hat{R}(k)^{\otimes m}\ket\psi_\mathrm{pol},
   \end{align}
   where,
   \begin{align}
   \hat{R}(\theta) = \left(\begin{array}{cc}
\cos\theta & -\sin\theta \\
\sin\theta & \cos\theta \end{array}\right).
   \end{align}
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U} \ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat{R}(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item Alice applies polarisation filters to $\ket\psi_\mathrm{comp}$, discarding horizontally polarised photons.
    \item The remaining vertically polarised state is Alice's unencrypted output of the computation.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics, using polarisation-key encoding.} \label{alg:homo_LO}
\end{table}

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.425\textwidth]{BS_homo}
\captionspacefig \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private-key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

Like polarisation rotations, uniform phase-shifts commute through linear optics networks, as per Eq.~(\ref{eq:LO_key_commute}), and thus the protocol has similar mathematical structure to the photonic case. Now the phase-shift angle, $\phi$, acts as Alice's private-key, which she applies uniformly to all input modes, applying inverse uniform phase-shifts after the computation to decrypt the state. The full algorithm is given in Alg.~\ref{alg:homo_coherent_LO}.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PhaseKeyEncoding($\vec\alpha$,$k$):
\begin{enumerate}
    \item Alice prepares the input multi-mode coherent state,
    \begin{align}
    \ket\psi_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m}.
    \end{align}
    \item Alice chooses a random private-key $k$ as a real number from the uniform distribution,
    \begin{align}
    k\in (0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same phase-shift, of angle $k$, to each mode,
    \begin{align}
    \ket\psi_\mathrm{enc} = \hat\Phi(k)^{\otimes m}\ket\psi_\mathrm{in},
    \end{align}
    where,
    \begin{align}
    \hat\Phi(\phi) = e^{i\phi\hat{n}},
    \end{align}
    is the phase-shift operator.
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat\Phi(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item The resulting state is,
    \begin{align}
    \ket\psi_\mathrm{comp} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m},
    \end{align}
    where,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on coherent state passive linear optics, using phase-key encoding.} \label{alg:homo_coherent_LO}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DisplacementKeyEncoding($\ket\psi$,$k$):
\begin{enumerate}
    \item Alice prepares the $m$-mode state $\ket\psi$.
    \item Alice chooses a set of independent complex displacement amplitudes as her private-key,
    \begin{align}
    k=\{\alpha_1,\dots,\alpha_m\}.
    \end{align}
    \item Alice applies the displacements to each mode, yielding her encrypted state,
    \begin{align}
    \ket\psi_\mathrm{enc} = \left[\bigotimes_{i=1}^m \hat{D}_i(\alpha_i)\right] \ket\psi,
    \end{align}
    where $\hat{D}_i(\alpha_i)$ is the displacement operator for the $i$th mode, with displacement amplitude $\alpha_i$.
    \item Alice sends the encrypted state to Bob.
    \item Bob applies the computation $\hat{U}$,
    \begin{align}
    \ket\psi_\mathrm{enc\, comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns the encrypted computed state to Alice.
    \item Alice calculates the inverse displacement amplitudes $\vec\beta$,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item Alice applies the inverse displacements to each mode,
    \begin{align}
    \ket\psi_\mathrm{comp} &= \left[\bigotimes_{i=1}^m \hat{D}^\dag_i(\beta_i)\right] \ket\psi_\mathrm{enc\, comp} \nonumber \\
    &= \hat{U}\ket\psi,
    \end{align}
    \item $\ket\psi_\mathrm{comp}$ is the unencrypted computed output state.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption using displacement-key encoding.} \label{alg:homo_disp_LO}
\end{table}

### 2018-10-26 Sections/essay_to_the_future_QKD.tex
Minor edits

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information theoretic security}).

The typical setting of QKD is as follows. There are two trusted parties who want to establish a secret key, Alice and Bob. They share two channels: a quantum channel, which allows them to send quantum states (encoded in photons or other states of light) to one another; and, a classical channel, with which they can send classical messages. The communication over the classical channel is assumed to be public and completely insecure, and the eavesdropper, Eve, has full anonymous access to it. However, Eve cannot modify messages shared over the classical channel.

>>>>

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret-key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information theoretic security}).

The typical setting of QKD is as follows. There are two trusted parties who want to establish a secret-key, Alice and Bob. They share two channels: a quantum channel, which allows them to send quantum states (encoded in photons or other states of light) to one another; and, a classical channel, with which they can send classical messages. The communication over the classical channel is assumed to be public and completely insecure, and the eavesdropper, Eve, has full anonymous access to it. However, Eve cannot modify messages shared over the classical channel.
